---
title: "**MOVEMENT IN THE PYROCENE: A GLOBAL META-ANALYSIS OF ANIMAL MOVEMENT RESPONSES TO FIRE**"
subtitle: "**Supplementary Material**"
written by: "**CL McAuley, EIF Wooster, TS Doherty, MA Cowan, CJ Jolly, GD Linley, DM Westaway, B Wilson, DG Nimmo**"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 4
    toc-title: "**Table of Contents**"
    output-file: "index.html"
    theme: simplex
    embed-resources: true
    code-fold: true
    code-tools: true
    number-sections: true
    #bibliography: ./bib/ref.bib
    fontsize: "12"
    max-width: "10"
    code-overflow: wrap
crossref: 
  fig-title: Figure     # (default is "Figure")
  tbl-title: Table     # (default is "Table")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Tab.    # (default is "Table")
editor_options: 
  chunk_output_type: console
execute:
  warning: false
  message: false
  tidy: true
  #cache: true
---

------------------------------------------------------------------------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(eval = FALSE)
```

## Dataset

```{r, echo = T}

kable(data, "html", escape = FALSE) %>% kable_styling("striped", position = "left", full_width = TRUE) %>%
  column_spec(66, width_min = "5in") %>%
  scroll_box(width = "100%",
    height = "500px")

```

## Setting up

### Loading Packages

```{r, echo = T}

# Loading Packages
pacman::p_load(devtools, 
               tidyverse, 
               metafor, 
               patchwork, 
               R.rsp, orchaRd,
               emmeans,
               metafor,
               orchaRd,
               stringr,
               dplyr,
               broom,
               tidyverse,
               here,
               broom,
               ggplot2,
               viridis,
               data.table,
               Matrix, 
               matrixcalc,
               ape, 
               multcomp 
) 


#for the model loops below

```

### Reading in Dataset and Phylogentic Tree

```{r, echo = T}

# Reading in Data
data <- read.csv(here("Outputs/Dat_for_MA_analysisRev5.csv")) 

# Reading in tree
tree1 <- read.tree(here("Outputs/Tree_fire-Rev4.tre")) 

# Getting branch length and correlation matrix
tree1b <- compute.brlen(tree1)
cor1 <-  vcv(tree1b, corr=T)

# checking the match, needs to return 0 
setdiff(dat$Species_tree, tree1$tip.label)

```

### Calculating Effect Sizes

```{r, echo = T}

# Calculating Hedge's G
es <- escalc(
  measure = "SMD",       
  m1i = Mean_Fire,
  sd1i = sd_Fire,
  n1i = Burned_n,
  m2i = Mean_Unburned,
  sd2i = sd_Unburned,
  n2i = Unburned_n,
  data = data,
  vtype = "UB")          

# Inspecting results
print(es) 

# Adding factor for obs level random effect
es$Obs_ID <- factor(1:nrow(es))

# Adding factor for study level random effect
es$StudyID <- NULL

es$Study_ID <- factor(as.numeric(as.factor(es$Firstauthor_Year)))

# Correcting direction of ES for Harris2020 tortuosity
es %>%
  dplyr::filter(Firstauthor_Year %in% c("Harris2020"))
  
es <- es %>%
  mutate(yi = ifelse(Obs_ID %in% c(91), yi * -1, yi))

```

### Correlation matrices to account for non-independence in models

```{r, echo = T}

# Matrix to account for non-independence in studies and observations
vcv <- vcalc(vi, cluster = Study_ID, obs = Obs_ID, rho = 0.5,
             data = es) 

```

## Meta-analysis {.tabset}

```{r, echo = T}
# Model
  mod.overall <- rma.mv(yi = yi, V = vcv,
                        random = list(~1 | Study_ID,
                                      ~1 | Species_tree, # phylo effect 
                                      ~1 | Species2, # non-phylo effect 
                                      ~1 | Obs_ID), 
                        data =  es,
                        control = list(optimizer="BFGS"),
                        test = "t",
                        sparse = TRUE,
                        R = list(Species_tree = cor1)
  )

summary(mod.overall)

dif <- orchard_plot(mod.overall, xlab = "Change in movement (Hedge's g)", group = "Study_ID",
                        angle = 0)

dif

round(i2_ml(mod.overall), 2)

```

## Meta-regression:Uni-moderator {.tabset}

### Movement Category

```{r, echo = T}
# Model
mod.overall_move <- rma.mv(yi = yi, V = vcv,
                             random = list(~1 | Study_ID,
                                           ~1 | Species_tree, # phylo effect 
                                           ~1 | Species2, # non-phylo effect 
                                           ~1 | Obs_ID), 
                             data =  es,
                             mods = ~ Movement_category -1,
                             control = list(optimizer="BFGS"),
                             test = "t",
                             sparse = TRUE,
                             R = list(Species_tree = cor1)
  )

summary(mod.overall_move)

movecatplot <- orchard_plot(mod.overall_move, xlab = "Change in movement (Hedge's g)", group = "Study_ID", mod = "Movement_category",angle = 0)

movecatplot

```

### Taxanomic Class

```{r, echo = T}
# Filtering out Amphibia due to small sample size
class.es <- es %>%
  filter(class_ncbi %in% c("Aves", "Mammalia", "Reptilia"))

class.es$class_ncbi <- factor(class.es$class_ncbi)

# VCV
class.vcv <- vcalc(vi, cluster = Study_ID, obs = Obs_ID, rho = 0.5,
                   data = class.es) 

# Model
mod.class <- rma.mv(yi = yi, V = class.vcv,
                      random = list(~1 | Study_ID,
                                    ~1 | Species_tree, # phylo effect 
                                    ~1 | Species2, # non-phylo effect 
                                    ~1 | Obs_ID), 
                      data =  class.es,
                      mods = ~ class_ncbi -1,
                      control = list(optimizer="BFGS"),
                      test = "t",
                      sparse = TRUE,
                      R = list(Species_tree = cor1)
  )

summary(mod.class)

classplot <- orchard_plot(mod.class, xlab = "Change in movement (Hedge's g)", 
                           group = "Study_ID", mod = "class_ncbi", angle = 0)

classplot

```

### Fire Type

```{r, echo = T}
# Filtering out not provided, unclear or both fire types
fire.es <- es %>%
  filter(Impact_fire_type %in% c("Planned", "Wildfire"))

fire.es$Impact_fire_type <- factor(fire.es$Impact_fire_type)

# VCV
fire.vcv <- vcalc(vi, cluster = Study_ID, obs = Obs_ID, rho = 0.5, 
                  data = fire.es) 

# Model
mod.fire <- rma.mv(yi = yi, V = fire.vcv,
                     random = list(~1 | Study_ID,
                                   ~1 | Species_tree, # phylo effect 
                                   ~1 | Species2, # non-phylo effect 
                                   ~1 | Obs_ID), 
                     data =  fire.es,
                     mods = ~ Impact_fire_type,
                     control=list(optimizer="BFGS"),
                     test = "t",
                     sparse = TRUE,
                     R = list(Species_tree = cor1)
  )

summary(mod.fire)

firetypeplot <- orchard_plot(mod.fire, xlab = "Change in movement (Hedge's g)", 
                          group = "Study_ID", mod = "Impact_fire_type", angle = 0)

firetypeplot
```

### Burn Extent

```{r, echo = T}

# Coercing variable to integer
size.es <- es %>%
  mutate(Impact_fire_size_ha = as.numeric(Impact_fire_size_ha) ) %>%
  mutate(Impact_fire_size_ha = as.integer(round(Impact_fire_size_ha)))

# Looking for NAs
summary(size.es$Impact_fire_size_ha)

# Removing NAs
size.es <- size.es[!is.na(size.es$Impact_fire_size_ha), ]

# Transforming data
size.es$log.size <- log(size.es$Impact_fire_size_ha)
hist(size.es$log.size)

#VCV 
size.vcv <- vcalc(vi, cluster = Study_ID, obs = Obs_ID, rho = 0.5,
                  data = size.es) 

# Model 
mod.size <- rma.mv(yi = yi, V = fire.vcv,
                     random = list(~1 | Study_ID,
                                   ~1 | Species_tree, # phylo effect 
                                   ~1 | Species2, # non-phylo effect 
                                   ~1 | Obs_ID), 
                     data =  size.es,
                     mods = ~ log.size, 
                     test = "t",
                     sparse = TRUE,
                     R = list(Species_tree = cor1)
  )
 
summary(mod.size)

newdat.size <- data.frame(log.size = seq(min(size.es$log.size, na.rm = TRUE),
                                         max(size.es$log.size, na.rm = TRUE),
                                         length.out = 100)) 

X.size <- model.matrix(~ log.size, data = newdat.size)[, -1, drop = FALSE]

preds.size <- predict(mod.size, newmods = X.size)

plot_data.size <- cbind(newdat.size, preds.size)

setDT(size.es)

size.es[, wi := 1/sqrt(vi)]
size.es[, pt_size := 2 + 7 * (wi-min(wi, na.rm = T)) / (max(wi, na.rm = T) - min(wi, na.rm = T))]
size.es

prey_age_text <- tidy(mod.size)
prey_age_text

p.size.mean <- ggplot()+
  # now add the rest of the points:
  geom_jitter(data = size.es, 
              aes(x = log.size, size = pt_size, 
                  y = yi),
              position = position_jitter(width = 0.01),
              inherit.aes = F,  alpha = 0.5)+
  geom_hline(yintercept = 0, lty = "dashed")+
  geom_ribbon(data = plot_data.size,
              aes(x = log.size,
                  ymin = pi.lb, ymax = pi.ub),
              fill = "transparent", color = "#dad7cd",
              alpha = .3)+
  geom_ribbon(data = plot_data.size, 
              aes(x = log.size,
                  ymin = ci.lb, ymax = ci.ub),
              alpha = .3)+
  geom_line(data = plot_data.size, 
            aes(x = log.size,
                y = pred),
            alpha = .8)+
  
  # coord_cartesian(ylim = c(-4, 4))+
  scale_size_identity()+
  theme_bw()+
  xlab("Log Burn Area (ha)")+
  ylab("Hedge's G")+
  theme(legend.position = "none",
        text = element_text(color = "black", family = "Helvetica"), axis.text = element_text(color = "black", family = "Helvetica"),
        panel.grid = element_blank(),
        panel.border = element_blank())

p.size.mean

```

### Time Since Fire

```{r, echo = T}

# Coercing variable to integer
es <- es %>%
  mutate(Maximum_treatment_burn_age_days = if_else(
    grepl("^[-]?[0-9]+$", Maximum_treatment_burn_age_days),
    as.integer(Maximum_treatment_burn_age_days),
    NA_integer_
  ))

# Looking for NAs
summary(es$Maximum_treatment_burn_age_days)

# Removing NAs
age.es <- es[!is.na(es$Maximum_treatment_burn_age_days), ]

# Transforming data
age.es$log.age <- log(age.es$Maximum_treatment_burn_age_days)
hist(age.es$log.age)

# Model
mod.age <- rma.mv(yi = yi, V = vcv,
                    random = list(~1 | Study_ID,
                                  ~1 | Species_tree, # phylo effect 
                                  ~1 | Species2, # non-phylo effect 
                                  ~1 | Obs_ID), 
                    data =  age.es,
                    mods = ~ log.age,
                    test = "t",
                    sparse = TRUE,
                    R = list(Species_tree = cor1)
  )

summary(mod.age)

newdat.age <- data.frame(log.age = seq(min(age.es$log.age, na.rm = TRUE),
                                       max(age.es$log.age, na.rm = TRUE),
                                       length.out = 100))

X.age <- model.matrix(~ log.age, data = newdat.age)[, -1, drop = FALSE]

preds.age <- predict(mod.age, newmods = X.age)

plot_data.age <- cbind(newdat.age, preds.age)

setDT(age.es)

age.es[, wi := 1/sqrt(vi)]
age.es[, pt_size := 2 + 7 * (wi-min(wi, na.rm = T)) / (max(wi, na.rm = T) - min(wi, na.rm = T))]
age.es

prey_age_text <- tidy(mod.age)
prey_age_text

p.age.mean <- ggplot()+
  # now add the rest of the points:
  geom_jitter(data = age.es, ## CM Changed this to age.es to due error "object 'yi' not found" - Matches the BM model
              aes(x = log.age, size = pt_size, 
                  y = yi),
              position = position_jitter(width = 0.01),
              inherit.aes = F,  alpha = 0.5)+
  geom_hline(yintercept = 0, lty = "dashed")+
  geom_ribbon(data = plot_data.age,
              aes(x = log.age,
                  ymin = pi.lb, ymax = pi.ub),
              fill = "transparent", color = "#dad7cd",
              alpha = .3)+
  geom_ribbon(data = plot_data.age, 
              aes(x = log.age,
                  ymin = ci.lb, ymax = ci.ub),
              alpha = .3)+
  geom_line(data = plot_data.age, 
            aes(x = log.age,
                y = pred),
            alpha = .8)+
  
  # coord_cartesian(ylim = c(-4, 4))+
  scale_size_identity()+
  theme_bw()+
  xlab("Log Maximum Burn Age (days)")+
  ylab("Hedge's G")+
  theme(legend.position = "none",
        text = element_text(color = "black", family = "Helvetica"), axis.text = element_text(color = "black", family = "Helvetica"),
        panel.grid = element_blank(),
        panel.border = element_blank())

p.age.mean

```

### Biome

```{r, echo = T}
# Filtering out biomes with <10 es
biome.es <- es %>%
  group_by(biome_name) %>%
  filter(n() >= 10) %>%
  ungroup()

table(biome.es$biome_name)

biome.es$biome_name <- factor(biome.es$biome_name)

# VCV
biome.vcv <- vcalc(vi, cluster = Study_ID, obs = Obs_ID, rho = 0.5,
                   data = biome.es) 

# Model
mod.biome <- rma.mv(yi = yi, V = biome.vcv,
                      random = list(~1 | Study_ID,
                                    ~1 | Species_tree, # phylo effect 
                                    ~1 | Species2, # non-phylo effect 
                                    ~1 | Obs_ID), 
                      data =  biome.es,
                      mods = ~ biome_name -1, 
                      control=list(optimizer="BFGS"),
                      test = "t",
                      sparse = TRUE,
                      R = list(Species_tree = cor1)
  )

summary(mod.biome)


biomeplot <- orchard_plot(mod.biome, xlab = "Change in movement (Hedge's g)", group = "Study_ID",
                           mod = "biome_name", angle = 0)

biomeplot

```

### Body Mass

```{r, echo = T}
#Transforming data
es$logmass <- log(es$BodyMass.g)

mod.bm <- rma.mv(yi = yi, V = vcv,
                   random = list(~1 | Study_ID,
                                 ~1 | Species_tree, # phylo effect 
                                 ~1 | Species2, # non-phylo effect 
                                 ~1 | Obs_ID), 
                   data =  es,
                   mods = ~ logmass,
                   control=list(optimizer="BFGS"),
                   test = "t",
                   sparse = TRUE,
                   R = list(Species_tree = cor1)
  )

summary(mod.bm)

newdat <- data.frame(logmass = seq(min(es$logmass, na.rm = TRUE),
                                   max(es$logmass, na.rm = TRUE),
                                   length.out = 100))

X <- model.matrix(~ logmass, data = newdat)[, -1, drop = FALSE]

preds <- predict(mod.bm, newmods = X)

plot_data <- cbind(newdat, preds)

setDT(es)

es[, wi := 1/sqrt(vi)]
es[, pt_size := 2 + 7 * (wi-min(wi, na.rm = T)) / (max(wi, na.rm = T) - min(wi, na.rm = T))]
es

prey_bm_text <- tidy(mod.bm)
prey_bm_text

p.bm.mean <- ggplot()+
  # now add the rest of the points:
  geom_jitter(data = es, 
              aes(x = logmass, size = pt_size, 
                  y = yi),
              position = position_jitter(width = 0.01),
              inherit.aes = F,  alpha = 0.5)+
  geom_hline(yintercept = 0, lty = "dashed")+
  geom_ribbon(data = plot_data,
              aes(x = logmass,
                  ymin = pi.lb, ymax = pi.ub),
              fill = "transparent", color = "#dad7cd",
              alpha = .3)+
  geom_ribbon(data = plot_data, 
              aes(x = logmass,
                  ymin = ci.lb, ymax = ci.ub),
              alpha = .3)+
  geom_line(data = plot_data, 
            aes(x = logmass,
                y = pred),
            alpha = .8)+
  
  # coord_cartesian(ylim = c(-4, 4))+
  scale_size_identity()+
  theme_bw()+
  xlab("Log body mass (g)")+
  ylab("Hedge's G")+
  theme(legend.position = "none",
        text = element_text(color = "black", family = "Helvetica"), axis.text = element_text(color = "black", family = "Helvetica"),
        panel.grid = element_blank(),
        panel.border = element_blank())

p.bm.mean

```

### Body Mass Mammals

```{r, echo = T}
# Filtering mammals
bm.mam.es <- es %>%
  filter(class_ncbi %in% c("Mammalia"))

#VCV
mam.vcv <- vcalc(vi, cluster = Study_ID, obs = Obs_ID, rho = 0.5, 
                 data = bm.mam.es) 

# Model
mod.bm.mam <- rma.mv(yi = yi, V = mam.vcv,
                       random = list(~1 | Study_ID,
                                     ~1 | Species_tree, # phylo effect 
                                     ~1 | Species2, # non-phylo effect 
                                     ~1 | Obs_ID), 
                       data =  bm.mam.es,
                       mods = ~ logmass,
                       control=list(optimizer="BFGS"),
                       test = "t",
                       sparse = TRUE,
                       R = list(Species_tree = cor1)
  )

summary(mod.bm.mam)

newdat.mam <- data.frame(logmass = seq(min(bm.mam.es$logmass, na.rm = TRUE),
                                       max(bm.mam.es$logmass, na.rm = TRUE),
                                       length.out = 100)) ## CM: Why is the length out 100?

X <- model.matrix(~ logmass, data = newdat.mam)[, -1, drop = FALSE]

preds.mam <- predict(mod.bm.mam, newmods = X)

plot_data.mam <- cbind(newdat.mam, preds.mam)

setDT(bm.mam.es)

bm.mam.es[, wi := 1/sqrt(vi)]
bm.mam.es[, pt_size := 2 + 7 * (wi-min(wi, na.rm = T)) / (max(wi, na.rm = T) - min(wi, na.rm = T))]
bm.mam.es

prey_bm.mam_text <- tidy(mod.bm.mam)
prey_bm.mam_text

p.bm.mam.mean <- ggplot()+
  # now add the rest of the points:
  geom_jitter(data = bm.mam.es, 
              aes(x = logmass, size = pt_size, 
                  y = yi),
              position = position_jitter(width = 0.01),
              inherit.aes = F,  alpha = 0.5)+
  geom_hline(yintercept = 0, lty = "dashed")+
  geom_ribbon(data = plot_data.mam,
              aes(x = logmass,
                  ymin = pi.lb, ymax = pi.ub),
              fill = "transparent", color = "#dad7cd",
              alpha = .3)+
  geom_ribbon(data = plot_data.mam, 
              aes(x = logmass,
                  ymin = ci.lb, ymax = ci.ub),
              alpha = .3)+
  geom_line(data = plot_data.mam, 
            aes(x = logmass,
                y = pred),
            alpha = .8)+
  
  # coord_cartesian(ylim = c(-4, 4))+
  scale_size_identity()+
  theme_bw()+
  xlab("Mammal Log body mass (g)")+
  ylab("Hedge's G")+
  theme(legend.position = "none",
        text = element_text(color = "black", family = "Helvetica"), axis.text = element_text(color = "black", family = "Helvetica"),
        panel.grid = element_blank(),
        panel.border = element_blank())

p.bm.mam.mean

```

### Body Mass Birds

```{r, echo = T}
# Filtering birds
bm.ave.es <- es %>%
  filter(class_ncbi %in% c("Aves"))

# VCV
aves.vcv <- vcalc(vi, cluster = Study_ID, obs = Obs_ID, rho = 0.5, # rho is usually 0.5 or 0.8
                  data = bm.ave.es) 

# Model
mod.bm.ave <- rma.mv(yi = yi, V = aves.vcv,
                       random = list(~1 | Study_ID,
                                     ~1 | Species_tree, # phylo effect 
                                     ~1 | Species2, # non-phylo effect 
                                     ~1 | Obs_ID), 
                       data =  bm.ave.es,
                       mods = ~ logmass,
                       control=list(optimizer="BFGS"),
                       test = "t",
                       sparse = TRUE,
                       R = list(Species_tree = cor1)
  )

summary(mod.bm.ave)

newdat.ave <- data.frame(logmass = seq(min(bm.ave.es$logmass, na.rm = TRUE),
                                       max(bm.ave.es$logmass, na.rm = TRUE),
                                       length.out = 100)) ## CM: Why is the length out 100?

X <- model.matrix(~ logmass, data = newdat.ave)[, -1, drop = FALSE]

preds.ave <- predict(mod.bm.ave, newmods = X)

plot_data.ave <- cbind(newdat.ave, preds.ave)

setDT(bm.ave.es)

bm.ave.es[, wi := 1/sqrt(vi)]
bm.ave.es[, pt_size := 2 + 7 * (wi-min(wi, na.rm = T)) / (max(wi, na.rm = T) - min(wi, na.rm = T))]
bm.ave.es

prey_bm.ave_text <- tidy(mod.bm.ave)
prey_bm.ave_text

p.bm.ave.mean <- ggplot()+
  # now add the rest of the points:
  geom_jitter(data = bm.ave.es, 
              aes(x = logmass, size = pt_size, 
                  y = yi),
              position = position_jitter(width = 0.01),
              inherit.aes = F,  alpha = 0.5)+
  geom_hline(yintercept = 0, lty = "dashed")+
  geom_ribbon(data = plot_data.ave,
              aes(x = logmass,
                  ymin = pi.lb, ymax = pi.ub),
              fill = "transparent", color = "#dad7cd",
              alpha = .3)+
  geom_ribbon(data = plot_data.ave, 
              aes(x = logmass,
                  ymin = ci.lb, ymax = ci.ub),
              alpha = .3)+
  geom_line(data = plot_data.ave, 
            aes(x = logmass,
                y = pred),
            alpha = .8)+
  
  # coord_cartesian(ylim = c(-4, 4))+
  scale_size_identity()+
  theme_bw()+
  xlab("Aves Log body mass (g)")+
  ylab("Hedge's G")+
  theme(legend.position = "none",
        text = element_text(color = "black", family = "Helvetica"), axis.text = element_text(color = "black", family = "Helvetica"),
        panel.grid = element_blank(),
        panel.border = element_blank())

p.bm.ave.mean

```

### Body Mass Reptiles

```{r, echo = T}
# Filtering reptiles
bm.rep.es <- es %>%
  filter(class_ncbi %in% c("Reptilia"))

# VCV
rep.vcv <- vcalc(vi, cluster = Study_ID, obs = Obs_ID, rho = 0.5,
                 data = bm.rep.es) 
# Model
mod.bm.rep <- rma.mv(yi = yi, V = rep.vcv,
                       random = list(~1 | Study_ID,
                                     ~1 | Species_tree, # phylo effect 
                                     ~1 | Species2, # non-phylo effect 
                                     ~1 | Obs_ID), 
                       data =  bm.rep.es,
                       mods = ~ logmass,
                       control=list(optimizer="BFGS"),
                       test = "t",
                       sparse = TRUE,
                       R = list(Species_tree = cor1)
  )

summary(mod.bm.rep)

newdat.rep <- data.frame(logmass = seq(min(bm.rep.es$logmass, na.rm = TRUE),
                                       max(bm.rep.es$logmass, na.rm = TRUE),
                                       length.out = 100)) 

X <- model.matrix(~ logmass, data = newdat.rep)[, -1, drop = FALSE]

preds.rep <- predict(mod.bm.rep, newmods = X)

plot_data.rep <- cbind(newdat.rep, preds.rep)

setDT(bm.rep.es)

bm.rep.es[, wi := 1/sqrt(vi)]
bm.rep.es[, pt_size := 2 + 7 * (wi-min(wi, na.rm = T)) / (max(wi, na.rm = T) - min(wi, na.rm = T))]
bm.rep.es

prey_bm.rep_text <- tidy(mod.bm.rep)
prey_bm.rep_text 

p.bm.rep.mean <- ggplot()+
  # now add the rest of the points:
  geom_jitter(data = bm.rep.es, 
              aes(x = logmass, size = pt_size, 
                  y = yi),
              position = position_jitter(width = 0.01),
              inherit.aes = F,  alpha = 0.5)+
  geom_hline(yintercept = 0, lty = "dashed")+
  geom_ribbon(data = plot_data.rep,
              aes(x = logmass,
                  ymin = pi.lb, ymax = pi.ub),
              fill = "transparent", color = "#dad7cd",
              alpha = .3)+
  geom_ribbon(data = plot_data.rep, 
              aes(x = logmass,
                  ymin = ci.lb, ymax = ci.ub),
              alpha = .3)+
  geom_line(data = plot_data.rep, 
            aes(x = logmass,
                y = pred),
            alpha = .8)+
  
  # coord_cartesian(ylim = c(-4, 4))+
  scale_size_identity()+
  theme_bw()+
  xlab("Reptilia Log body mass (g)")+
  ylab("Hedge's G")+
  theme(legend.position = "none",
        text = element_text(color = "black", family = "Helvetica"), axis.text = element_text(color = "black", family = "Helvetica"),
        panel.grid = element_blank(),
        panel.border = element_blank())

p.bm.rep.mean

```

## Publication bias testing predator-prey {.tabset}

### Decline effect for difference

```{r, echo = T}

str(es$Publication_Year)

mod_mad <- rma.mv(yi = yi, V = vcv,
                  random = list(~1 | Study_ID,
                                ~1 | Species_tree, # phylo effect 
                                ~1 | Species2, # non-phylo effect 
                                ~1 | Obs_ID), 
                  data = es,
                  mods = ~ Publication_Year,
                  control=list(optimizer="BFGS"),
                  test = "t",
                  sparse = TRUE,
                  R = list(Species_tree = cor1)
)

summary(mod_mad)

decline <- bubble_plot(mod_mad,
                       mod = "Publication_Year",
                       group = "Study_ID",
                       xlab = "Publication year",
                       ylab = "Hedge's g",
                       g = TRUE,
                       weights = 1/sqrt(es$vi))

decline

```

### Eggers regression + funnel

```{r, echo = T}

es$effectN <- (es$Unburned_n * es$Burned_n) / (es$Unburned_n + es$Burned_n)
es$sqeffectN <- sqrt(es$effectN)

mod_diff_egg <- rma.mv(yi = yi, V = vcv,
                         random = list(~1 | Study_ID,
                                       ~1 | Species_tree, # phylo effect 
                                       ~1 | Species2, # non-phylo effect 
                                       ~1 | Obs_ID), 
                         data =  es,
                         mods = ~ sqeffectN,
                         control=list(optimizer="BFGS"),
                         test = "t",
                         sparse = TRUE,
                         R = list(Species_tree = cor1)
  )
  summary(mod_diff_egg)

funnel(mod_diff_egg, 
       yaxis="seinv",
       xlab = "Standardized residuals",
       ylab = "Precision (inverse of SE)",
       
)
```

### Leave one out

```{r, echo = T, eval = FALSE}

es$Firstauthor_Year <- as.factor(es$Firstauthor_Year)

es$leave_out <- as.factor(es$Firstauthor_Year)

LeaveOneOut_effectsize <- list()
for (i in 1:length(levels(es$leave_out))) {
  temp_dat <- es %>%
    dplyr::filter(leave_out != levels(es$leave_out)[i])
  
  VCV_leaveout <- vcalc(vi = temp_dat$vi, cluster = temp_dat$Study_ID, obs = temp_dat$Obs_ID, rho = 0.5)
  
  LeaveOneOut_effectsize[[i]] <-  rma.mv(yi = yi, V = VCV_leaveout,
                                         random = list(~1 | Study_ID,
                                                       ~1 | Species_tree, # phylo effect 
                                                       ~1 | Species2, # non-phylo effect 
                                                       ~1 | Obs_ID), 
                                         control=list(optimizer="BFGS"),
                                         test = "t",
                                         method = "REML", 
                                         sparse = TRUE,
                                         R = list(Species_tree = cor1),
                                         data = temp_dat[temp_dat$leave_out != levels(temp_dat$leave_out)[i], ])
}


# Writing function for extracting est, ci.lb, and ci.ub from all models
est.func <- function(model) {
  df <- data.frame(est = model$b, lower = model$ci.lb, upper = model$ci.ub)
  return(df)
}

# Using dplyr to form data frame
MA_oneout <- lapply(LeaveOneOut_effectsize,function(x) est.func(x)) %>%
  bind_rows %>%
  mutate(left_out = levels(es$leave_out))

# Telling ggplot to stop reordering factors
MA_oneout$left_out <- as.factor(MA_oneout$left_out)
MA_oneout$left_out <- factor(MA_oneout$left_out, levels = MA_oneout$left_out)

# Saving the runs
saveRDS(MA_oneout, here("Outputs/No_space_use", "MA_oneout.RDS"))


```

```{r, echo = F}
MA_oneout <- readRDS(here("Outputs/No_space_use", "MA_oneout.RDS"))

leaveoneout <- ggplot(MA_oneout) + geom_hline(yintercept = 0, lty = 2, lwd = 1) +
  geom_hline(yintercept = mod.overall$ci.lb, lty = 3, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = mod.overall$b, lty = 1, lwd = 0.75, colour = "black") + 
  geom_hline(yintercept = mod.overall$ci.ub,
             lty = 3, lwd = 0.75, colour = "black") + 
  geom_pointrange(aes(x = left_out, y = est,
                      ymin = lower, ymax = upper)) + 
  xlab("Study left out") + 
  ylab("Difference in logit overlap (logit)") +
  coord_flip() + 
  theme(panel.grid.minor = element_blank()) + theme_bw() + theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor.x = element_blank()) + theme(axis.text.y = element_text(size = 6))

leaveoneout

```

## R Session Information

```{r, echo = T}
# pander for making it look nicer
sessionInfo() %>% pander()
```
